A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-08-24 tex/paper.tex
WASP PHOENIX work

While the CfA grid spectra fit well with no obvious features in the residual spectrum, because the PHOENIX spectrum is computed over a very broad spectral range and there is no tuning for specific stars like the Sun, there are often a small amount of  ``outlier'' lines that appear in the residual spectrum (e.g., \citealt{husser13}, Figure 8). Because sigma-clipping is a procedure, it is impossible to quantify the effect that clipping a given line has on the final parameter estimates \citep{hogg10}. For example, what if a series of lines with $\sim$3 sigma disagreement actually has substantial discriminatory power against the stellar parameters? \todo{Might be unnecessary from all that we wrote in section 3?}

This behaviour motivates the global and local kernels in a more sophisticated likelihood function, which includes a mechanism to account for the systematic mismatch of data spectrum and model spectrum.  The amplitude and scale of the global covariance grows to capture the discrepancy between data spectrum and synthetic spectrum. Including this global covariance broadens the posteriors on the stellar parameters, providing cushion against the outlier lines.  The global covariance acts as a way to parameterize the goodness or badness of a fit: better spectral models will have a lower covariance, as evidenced by the global covariance amplitudes between the {\sc CfA/Kurucz} and {\sc Phoenix} libraries (Tables~\ref{table:Kurucz}~\&~\ref{table:PHOENIX}).

Local covariance kernels track outlier spectral lines. These kernels can map out the regions of the spectrum which are outliers. The glory of these local kernels are that the parameters allow to play a role in data driven spectra. \emph{A priori} we do not know which regions of the spectrum are improperly modeled. The covariance hyperparameters provide a framework to identify these regions iteratively and in a self-consistent manner.  See Figure~\ref{fig:residuals_PHOENIX} for a demonstration of how the local kernels identify and track spectral line outliers.

Comparing the results in Tables~\ref{table:Kurucz}~\&~\ref{table:PHOENIX} reveal that there is a systematic offset depending on which spectral library is used as a backend. Depending on your assumptions, there may be systematic differences of 200K or more in $T_{\rm eff}$.

>>>>

While the CfA grid spectra fit well with no obvious features in the residual spectrum, because the PHOENIX spectrum is computed over a very broad spectral range with no specific tuning for solar type stars, there are likely to be a small amount of  ``outlier'' lines that appear in the residual spectrum (e.g., \citealt{husser13}, Figure 8). Some routines choose to ``sigma-clip'' the outlier lines and procede with fitting, however with such an approach it is difficult to quantify the effect that clipping a given line has on the final parameter estimates \citep{hogg10}. For example, what if a series of lines with $\sim$3 sigma disagreement actually has substantial discriminatory power against the stellar parameters?

This behaviour motivates the global and local kernels in a more sophisticated likelihood function, which includes a mechanism to account for the systematic mismatch of data spectrum and model spectrum.  The amplitude and scale of the global covariance grows to capture the discrepancy between data spectrum and synthetic spectrum. Including this global covariance broadens the posteriors on the stellar parameters, providing cushion against the outlier lines.

Using the {\sc Phoenix} models on WASP-14, we infer substantially different posteriors than with using the {\sc CfA/Kurucz} library. Figure~\ref{fig:PHOENIX_posterior} displays some of the relevant marginal posteriors, and Table~\ref{table:PHOENIX} compiles the estimates of the peaks of the posterior distribution and associated confidence intervals. Figure~\ref{fig:residuals_PHOENIX} demonstrates the quality of this approach and the structure of the associated residuals. Compared to the Kurucz residuals in Figure~\ref{fig:residuals_Kurucz}, there are two significant differences. First, the amplitude of the global covariance structure is larger. The global covariance acts as a way to parameterize the goodness or badness of a fit: better spectral models will have a lower covariance. Second, local covariance kernels track outlier spectral lines. These kernels can map out the regions of the spectrum which are outliers. The covariance hyperparameters provide a framework to identify these regions iteratively and in a self-consistent manner. The locations and amplitudes of these kernels output from the code would be useful information to consider when refining the models of stellar sythenis.

Comparing the results in Tables~\ref{table:Kurucz}~\&~\ref{table:PHOENIX} reveals that there is a systematic offset depending on which spectral library is used as a backend. Depending on the choice of spectral library, there may be systematic differences of 200 K or more in $T_{\rm eff}$ and 0.2 dex or more in $\Z$.
